% !TeX program = lualatex
% !TeX encoding = UTF-8
% !TeX spellcheck = en_US

% Copyright (C) 2022 myl7
% SPDX-License-Identifier: CC-BY-SA-4.0

\documentclass{article}

% Lua code helper
\usepackage{luacode}

% Margins
\usepackage[margin=2cm]{geometry}

% No indent
% \usepackage{parskip}
% \setlength{\parindent}{0px}

% Chinese fonts
% \usepackage{luatexja-fontspec}
% \setmainjfont{Noto Sans CJK SC}

% Random text for debug
% \usepackage{blindtext}

% Multiple column env
\usepackage{multicol}

% List config helper
\usepackage{enumitem}

% Specify font encoding to avoid composed characters
\usepackage[T1]{fontenc}

% Specify fonts
\usepackage{fontspec}
% \setmainfont{DejaVu Serif}
% \setsansfont{DejaVu Sans}
% Require manual installation of DM Mono
% \setmonofont{DM Mono}
% Use sans font by default
% \renewcommand{\familydefault}{\sfdefault}
% For pretty programming language names
% Require package ttf-liberation on Alpine
\newfontface\fontfaceLiberationSerif{Liberation Serif}

% Hyperlinks
% Pls ensure it is the last imported one
\usepackage{hyperref}
\hypersetup{colorlinks=true}

% Erase link color in printing
\usepackage[ocgcolorlinks]{ocgx2}

% No page number since this has only 1 page
\pagenumbering{gobble}

% Pretty C++ from https://isocpp.org/wiki/faq/misc-environmental-issues#latex-macros
\newcommand{\Cpp}{C\nolinebreak[4]\hspace{-.05em}\raisebox{.4ex}{\tiny\bf ++}}
% Pretty C# from https://tex.stackexchange.com/a/44537
\newcommand{\Csharp}{C{\fontfaceLiberationSerif\#}}

\begin{document}

\begin{center}
  {\huge \textbf{Yulong Ming}}
\end{center}

\begin{multicols}{2}
  [\section*{Profile}]
  PhD student (2022--26) in Computer Science at City University of Hong Kong interested in Network Security, including Metadata Privacy.
  FLOSS (free/libre and open-source software) enthusiast believing that \href{https://www.gnu.org/philosophy/saying-no-even-once.html}{even once is help}.
  GitHub active code contributor with over 500 contributions per year.
  Linux fan running Arch Linux for everyday use.
  He/him.

  \begin{itemize}[itemsep=0cm,parsep=0cm]
    \item GitHub: \href{https://github.com/myl7}{github.com/myl7}
    \item Homepage: \href{https://myl.moe}{myl.moe}
    \item Emails:
    \begin{itemize}[itemsep=0cm,parsep=0cm,topsep=0cm,leftmargin=0.25cm,label=\labelitemiii]
      \item \href{mailto:myl.7@my.cityu.edu.hk}{myl.7@my.cityu.edu.hk} (academic)
      \item \href{mailto:myl@myl.moe}{myl@myl.moe} (code dev)
      \item \href{mailto:myl7.moe@gmail.com}{myl7.moe@gmail.com} (general)
    \end{itemize}
    \item Address: Office G7308\#8, Yeung Kin Man Academic Building, City University of Hong Kong, Hong Kong
  \end{itemize}
\end{multicols}

\hrule

\section*{Education}
\begin{itemize}[parsep=0.1cm,leftmargin=0.4cm]
  \item PhD in CS at City University of Hong Kong\ \dotfill\ 2022--26, Hong Kong
  \begin{itemize}[itemsep=0cm,parsep=0cm,topsep=0cm,leftmargin=0.25cm,label=\labelitemiii]
    \item Advisors: \href{https://www.cs.cityu.edu.hk/~jia/}{Prof. Xiaohua Jia}, \href{https://www.cs.cityu.edu.hk/~congwang/}{Prof. Cong Wang}
  \end{itemize}
  \item BSc in CS at University of Science and Technology of China\ \dotfill\ 2018--22, Hefei, China
\end{itemize}

\section*{Publications}
\begin{itemize}[parsep=0.1cm,leftmargin=0.4cm]
  \item A submitted paper on cross-shard optimization in blockchain, NSDI {\textquotesingle}23 Fall\ \dotfill\ 07--09/2022, Hong Kong
  \begin{itemize}[itemsep=0cm,parsep=0cm,topsep=0cm,leftmargin=0.25cm,label=\labelitemiii]
    \item I carried out the whole experiment, including code implementation, evaluation, and data analysis.
  \end{itemize}
\end{itemize}

\section*{Experiences}
\begin{itemize}[parsep=0.1cm,leftmargin=0.4cm]
  \item Core member \& former CTO of \href{https://lug.ustc.edu.cn/}{USTCLUG}\ \dotfill\ 2019--22, Hefei, China
    \begin{itemize}[itemsep=0cm,parsep=0cm,topsep=0cm,leftmargin=0.25cm,label=\labelitemiii]
      \item USTCLUG is one of China's earliest and most well-known Linux groups (not limited to students).
      \item I participated in the development/leadership of various USTCLUG projects, e.g., \href{https://vlab.ustc.edu.cn/}{VLAB}, \href{https://mirrors.ustc.edu.cn/}{USTC Software Mirror}, its \href{https://summer-ospp.ac.cn/}{OSPP} projects, and the hardware infrastructure.
    \end{itemize}
\end{itemize}

\section*{Abilities}
\begin{itemize}[parsep=0.1cm,leftmargin=0.4cm]
  \item \textbf{Programming languages}:
    I have production experience with Python (Django), Rust, Go, JavaScript+TypeScript (React, Next.js).
    I can also write \Cpp{} (basic modern \Cpp), C, Shell script, \LaTeX, Java, Verilog, and \Csharp{} (sorted by familiarity).
  \item \textbf{Natural languages}: Mandarin Chinese (mother tongue), English, Japanese (elementary listening only).
\end{itemize}

\end{document}
